Finite Time Analysis of Linear Stochastic Approximation

### 2017-05-06 not.tex
initial version

We denote the sets real and complex number by $\R$ and $\C$ respectively. For $x=a+ib\in \C$, we denote its real and imaginary parts by $\re{x}=a$ and $\im{x}=b$ respectively. We denote $n$-dimensional vector spaces over $\R$ and $\C$ by $\R^{n}$ and $\C^{n}$ respectively. We use $\R^{\ncn}$ and $\C^{\ncn}$ to denote $\ncn$ matrices with real and complex entries respectively. For any $x\in \C$ we denote the modulus of $x$ by $\md{x}=\sqrt{\re{x}^2+\im{x}^2}$. For any $x\in \C^n$We denote complex conjugate of $x$ by $\bar{x}$. We denote the transpose of $x\in \C^{n}, A\in \C^{\ncn}$ by $x^\top$ and $A^\top$ respectively. Further, by $x^\dag$ denotes the conjugate transpose, i.e., $x^\dag=\bar{x}^\top$ (the same convention carries over to matrices as well). We will use $\ip{\cdot,\cdot}$ to denote the inner products: $\ip{x,y}=x^\dag y$. Also, by $A_{ij}$ we denote the entry of matrix $A$ in the $i^{th}$ row and $j^{th}$ column.
The norm of the matrix $A$ in given by $\norm{A}\eqdef \sup_{x\in \C^n:\norm{x}=1} \norm{Ax}$. For a positive real number $B>0$, we denote by $\C^{\ncn}_B=\{A\in \C^{\ncn}\mid \norm{A}\leq B\}$ and  $\R^{\ncn}_B=\{A\in \R^{\ncn}\mid \norm{A}\leq B,\,\forall i,j=1,\ldots,n\}$ the set of complex and real matrices whose norms are bounded $B$.
%We denote by $\C^{\ncn}_B=\{A\in \C^{\ncn}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$ and  $\R^{\ncn}_B=\{A\in \R^{\ncn}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$.
%We use $\P$ to denote the set of probability distribution over $\C^{\ncn}$.
We also denote the set of invertible $\ncn$ complex matrices by $\gln$. We use $A\sim P$ to denote the fact that the random variable $A$ is distributed according to distribution $P$. Let the random matrix $A\sim P$, and $U\in \gln$, we use $P_U$ to denote the distribution of the random matrix $U^{-1}A U$.  We denote the identity matrix in $\C^{\ncn}$ by $\I$.
%We denote the set of distributions over $\C_B^{\ncn}$ by $\P$.

We use $A\succeq 0$ to denote that the
square matrix $A$ is hermitian and positive semidefinite (HPD):
$A = A^\dag$, $\inf_x x^\dag A x\ge 0$.
For $A,B$ HPD matrices, $A\succeq B$ holds if $A-B\succeq 0$.
We also use $A\succ B$ similarly to denote that $A-B \succ 0$.
We also use $\preceq$ and $\prec$ analogously. For any $x\in\C^n$x, we denote the general quadratic norm with respect to a $C\succ 0$ by $\norm{x}^2_C\eqdef x^\dag\, C \,x$.
$\E$ denotes mathematical expectation.

\begin{definition}
Let $P$ be a distribution over $\C^{\ncn}$, then define
\begin{align*}
A_P=\int M dP(M),\quad C_P=\int M^\dag M dP(M),
\end{align*}
\end{definition}
\begin{definition}\label{def:contract}[Contraction Factors]
Define
\begin{align*}
\rhod{P}&\eqdef {\inf}_{x\in\C^n\colon\norm{x}=1}\ip{x,\left((A_P+A_P^\dag)-\alpha A_P^\dag A_P\right)x},\\ \rhos{P}&\eqdef{\inf}_{x\in \C^n\colon\norm{x}=1}\ip{x,\left((A_P+A_P^\dag)-\alpha C_P\right)x}
\end{align*}
\end{definition}
Note that $\rhod{P}>\rhos{P}$.

\begin{definition}
We call a matrix $A\in \C^{\ncn}$ to be \emph{positive definite} (PD) if $\ip{x,Ax} >0,\,\forall x\neq 0 \in \C^{n}$. We call a matix $A\in \C^{\ncn}$ to be \emph{asymptotically stable} (AS) if all eigenvalues of $A$ have positive real parts. We call a matrix $A\in \C^{\ncn}$ to be \emph{symmetric positive definite} (SPD) is it is symmetric i.e., $A^\top=A$ and PD.
\end{definition}
\begin{definition}\label{distpd}
We call a distribution $P$ to be PD/AS/SPD if $A_P$ is PD/AS/SPD.
\end{definition}

>>>>

We denote the sets real and complex number by $\R$ and $\C$ respectively. For $x=a+ib\in \C$, we denote its real and imaginary parts by $\re{x}=a$ and $\im{x}=b$ respectively. We denote $n$-dimensional vector spaces over $\R$ and $\C$ by $\R^{d}$ and $\C^{d}$ respectively. We use $\R^{\dcd}$ and $\C^{\dcd}$ to denote $\dcd$ matrices with real and complex entries respectively. For any $x\in \C$ we denote the modulus of $x$ by $\md{x}=\sqrt{\re{x}^2+\im{x}^2}$. For any $x\in \C^d$We denote complex conjugate of $x$ by $\bar{x}$. We denote the transpose of $x\in \C^{d}, A\in \C^{\dcd}$ by $x^\top$ and $A^\top$ respectively. Further, by $x^*$ denotes the conjugate transpose, i.e., $x^*=\bar{x}^\top$ (the same convention carries over to matrices as well). We will use $\ip{\cdot,\cdot}$ to denote the inner products: $\ip{x,y}=x^* y$. Also, by $A_{ij}$ we denote the entry of matrix $A$ in the $i^{th}$ row and $j^{th}$ column.
The norm of the matrix $A$ in given by $\norm{A}\eqdef \sup_{x\in \C^d:\norm{x}=1} \norm{Ax}$. For a positive real number $B>0$, we denote by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \norm{A}\leq B\}$ and  $\R^{\dcd}_B=\{A\in \R^{\dcd}\mid \norm{A}\leq B,\,\forall i,j=1,\ldots,n\}$ the set of complex and real matrices whose norms are bounded $B$.
%We denote by $\C^{\dcd}_B=\{A\in \C^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$ and  $\R^{\dcd}_B=\{A\in \R^{\dcd}\mid \md{A_{ij}}\leq B,\,\forall i,j=1,\ldots,n\}$.
%We use $\P$ to denote the set of probability distribution over $\C^{\dcd}$.
We also denote the set of invertible $\dcd$ complex matrices by $\gln$. We use $A\sim P$ to denote the fact that the random variable $A$ is distributed according to distribution $P$. Let the random matrix $A\sim P$, and $U\in \gln$, we use $P_U$ to denote the distribution of the random matrix $U^{-1}A U$.  We denote the identity matrix in $\C^{\dcd}$ by $\I$.
%We denote the set of distributions over $\C_B^{\dcd}$ by $\P$.

We use $A\succeq 0$ to denote that the
square matrix $A$ is hermitian and positive semidefinite (HPD):
$A = A^*$, $\inf_x x^* A x\ge 0$.
For $A,B$ HPD matrices, $A\succeq B$ holds if $A-B\succeq 0$.
We also use $A\succ B$ similarly to denote that $A-B \succ 0$.
We also use $\preceq$ and $\prec$ analogously. For any $x\in\C^d$x, we denote the general quadratic norm with respect to a $C\succ 0$ by $\norm{x}^2_C\eqdef x^*\, C \,x$.
$\E$ denotes mathematical expectation.

\begin{definition}
Let $P$ be a distribution over $\C^{\dcd}$, then define
\begin{align*}
A_P=\int M dP(M),\quad C_P=\int M^* M dP(M),
\end{align*}
\end{definition}
\begin{definition}\label{def:contract}[Contraction Factors]
Define
\begin{align*}
\rhod{P}&\eqdef {\inf}_{x\in\C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha A_P^* A_P\right)x},\\ \rhos{P}&\eqdef{\inf}_{x\in \C^d\colon\norm{x}=1}\ip{x,\left((A_P+A_P^*)-\alpha C_P\right)x}
\end{align*}
\end{definition}
Note that $\rhod{P}>\rhos{P}$.

\begin{definition}
We call a matrix $A\in \C^{\dcd}$ to be \emph{positive definite} (PD) if $\ip{x,Ax} >0,\,\forall x\neq 0 \in \C^{d}$. We call a matix $A\in \C^{\dcd}$ to be \emph{asymptotically stable} (AS) if all eigenvalues of $A$ have positive real parts. We call a matrix $A\in \C^{\dcd}$ to be \emph{symmetric positive definite} (SPD) is it is symmetric i.e., $A^\top=A$ and PD.
\end{definition}
\begin{definition}\label{distpd}
We call a distribution $P$ to be PD/AS/SPD if $A_P$ is PD/AS/SPD.
\end{definition}
\begin{example}
The matrices $\begin{bmatrix}0.1 &-1\\ 1 & 0.1\end{bmatrix}$, $\begin{bmatrix} 0.1 & 0.1 \\ 0 & 0.1\end{bmatrix}$ and $\begin{bmatrix}0.1 &0 \\ 0 & 0.1\end{bmatrix}$ are examples of AS, PD and SPD respectively.
\end{example}

### 2017-05-06 prob.tex
initial version

\section{Problem Setup}
We consider the linear stochastic approximation (LSA) algorithm with constant step size and PR-averaging of the iterates.
\begin{subequations}\label{eq:lsa}
\begin{align}
\label{conststep}&\text{LSA:} &\theta_t&=\theta_{t-1}+\alpha(b_t-A_t\theta_{t-1}),\\
\label{iteravg}&\text{PR-Average:} &\thh_t&=\frac{1}{t+1}{\sum}_{s=0}^{t}\theta_i,
\end{align}
\end{subequations}
where $\thh_t, \theta_t \in \C^{n}$. The algorithm updates a pair of parameters $\theta_t,\tb_t\in \C^{\ncn}$ incrementally, in discrete time steps $t=1,2,\dots$
based on data $b_t\in \C^n$, $A_t\in \C^{n\times n}$\footnote{In almost all practical instances, the iterates $\theta_t,\thh_t\in \R^n$ and $A_t\in \R^{\ncn}, b_t\in \R^n$. However, it serves well for our analysis to make the general assumption that these qunatites are complex valued.}. Here $\alpha>0$ is a positive step-size parameter; the only tuning parameter of the algorithm besides the
initial value $\theta_0$. The iterate $\theta_t$ is treated as an internal state of the algorithm, while $\th_t$ is the output at time step $t$. The update of $\theta_t$ alone is considered a form of constant stepsize LSA. Note that the computation of $\theta_t$ can also be performed in an incremental fashion using $O(n)$ storage.

@@

\item \label{dist} $\{A_t\in\C^{\ncn},\, t\geq 0\}$ is an $i.i.d$ sequence distributed according to $P$ which is either AS or PD or SPD.
\item $\{b_t\}$ is an $i.i.d$ sequence of vectors in $\C^n$ with mean $\E[b_t]=b$.

@@

%\begin{align*}\E\left[ M_t^\dag M_t\mid\F_{t-1}\right]\leq \Sigma^2_P, \, \E[N_t^\dag N_t]=\sigma_b^2.\end{align*}
\begin{align*}\E\left[ \norm{M_t}^2\mid\F_{t-1}\right]\leq \sigma^2_P, \, \E[N_t^\dag N_t]=\sigma_b^2.\end{align*}

@@

where recall that for a SPD matrix $C$, $\norm{x}_C^2 = x^\dag C x$. Here, the choice of the matrix $C$ depends on the application.\\

>>>>

\section{Problem Setup}
We consider the linear stochastic approximation (LSA) algorithm with constant step size and PR-averaging of the iterates.
\begin{subequations}\label{eq:lsa}
\begin{align}
\label{conststep}&\text{LSA:} &\theta_t&=\theta_{t-1}+\alpha(b_t-A_t\theta_{t-1}),\\
\label{iteravg}&\text{PR-Average:} &\thh_t&=\frac{1}{t+1}{\sum}_{s=0}^{t}\theta_i,
\end{align}
\end{subequations}
where $\thh_t, \theta_t \in \C^{d}$. The algorithm updates a pair of parameters $\theta_t,\tb_t\in \C^{\dcd}$ incrementally, in discrete time steps $t=1,2,\dots$
based on data $b_t\in \C^d$, $A_t\in \C^{n\times n}$\footnote{In almost all practical instances, the iterates $\theta_t,\thh_t\in \R^d$ and $A_t\in \R^{\dcd}, b_t\in \R^d$. However, it serves well for our analysis to make the general assumption that these qunatites are complex valued.}. Here $\alpha>0$ is a positive step-size parameter; the only tuning parameter of the algorithm besides the
initial value $\theta_0$. The iterate $\theta_t$ is treated as an internal state of the algorithm, while $\th_t$ is the output at time step $t$. The update of $\theta_t$ alone is considered a form of constant stepsize LSA. Note that the computation of $\theta_t$ can also be performed in an incremental fashion using $O(n)$ storage.

@@

\item \label{dist} $\{A_t\in\C^{\dcd},\, t\geq 0\}$ is an $i.i.d$ sequence distributed according to $P$ which is either AS or PD or SPD.
\item $\{b_t\}$ is an $i.i.d$ sequence of vectors in $\C^d$ with mean $\E[b_t]=b$.

@@

%\begin{align*}\E\left[ M_t^* M_t\mid\F_{t-1}\right]\leq \Sigma^2_P, \, \E[N_t^* N_t]=\sigma_b^2.\end{align*}
\begin{align*}\E\left[ \norm{M_t}^2\mid\F_{t-1}\right]\leq \sigma^2_P, \, \E[N_t^* N_t]=\sigma_b^2.\end{align*}

@@

where recall that for a SPD matrix $C$, $\norm{x}_C^2 = x^* C x$. Here, the choice of the matrix $C$ depends on the application.\\

### 2017-05-06 related.tex
initial version

\section{Related Work}
\subsection{Linear Regression}
Let $(x_t,y_t)\in \R^n\times \R,\,t\geq 1$ be $i.i.d$ such that $\EE{\norm{x_t}^2}$ and $\EE{y_t^2}$ are finite. Further, we assume bounded data i.e., $\norm{(x_t,y_t)}^2\leq B$ for some positive real number $B>0$. Here, $x_t,\,t\geq 1$ are the features and $y_t$ are real labels and the linear regression problem constitutes minimizing the quadratic loss function $f(\theta)=\EE{\left(\ip{x_t,\theta}-y_t\right)^2}$. The stochastic gradient descent scheme with constant step size $\alpha>0$ to minimize $f(\theta)$ can be given as below:
\begin{align}\label{linreg}
\theta_t=\theta_{t-1}-\alpha x_t\left(\ip{x_t,\theta_{t-1} -y_t}\right)
\end{align}
Here $\nabla f(\theta_{t-1})=x_t\left(\ip{x_t,\theta_{t-1} -y_t}\right)$ is the \emph{stochastic gradient} of the objective $f(\theta)$. It follows from the $i.i.d$ assumption on $(x_t,y_t)$ that $A_t=x_t x_t^\top$ and $b_t=y_t x_t$ are also $i.i.d$, and with this identification one can see that \eqref{linreg} is of the form in \eqref{conststep}. In this case $A_P$ is SPD.
In the linear regression setting, the error of a parameter $\theta$ is measured as the difference between the loss at the said parameter and the loss at the optimum, which has the following form
\begin{align*}
f(\theta)-f(\ts)=(\theta-\ts)^\top A_P (\theta-\ts)=\EE{\norm{\theta-\ts}^2_{A_P}}
\end{align*}

\subsection{Reinforcement Learning}

\paragraph{RL Setting}
We are presented with data in the form of an $i.i.d$ sequence $(\phi_t,\phi'_t,r_t)\in \R^n\times\R^n\times \R$. Let $\gamma \in (0,1)$ be a fixed constant, we define $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$ the various temporal difference learning algorithms can be written as in \Cref{table:td}. In what follows, $\rho_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\rho_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\rho_t>0$ is known as \emph{off-policy}.}.
\begin{comment}
\begin{table}

>>>>

\section{Related Work}
\begin{comment}
\subsection{Linear Regression}
Let $(x_t,y_t)\in \R^d\times \R,\,t\geq 1$ be $i.i.d$ such that $\EE{\norm{x_t}^2}$ and $\EE{y_t^2}$ are finite. Further, we assume bounded data i.e., $\norm{(x_t,y_t)}^2\leq B$ for some positive real number $B>0$. Here, $x_t,\,t\geq 1$ are the features and $y_t$ are real labels and the linear regression problem constitutes minimizing the quadratic loss function $f(\theta)=\EE{\left(\ip{x_t,\theta}-y_t\right)^2}$. The stochastic gradient descent scheme with constant step size $\alpha>0$ to minimize $f(\theta)$ can be given as below:
\begin{align}\label{linreg}
\theta_t=\theta_{t-1}-\alpha x_t\left(\ip{x_t,\theta_{t-1} -y_t}\right)
\end{align}
Here $\nabla f(\theta_{t-1})=x_t\left(\ip{x_t,\theta_{t-1} -y_t}\right)$ is the \emph{stochastic gradient} of the objective $f(\theta)$. It follows from the $i.i.d$ assumption on $(x_t,y_t)$ that $A_t=x_t x_t^\top$ and $b_t=y_t x_t$ are also $i.i.d$, and with this identification one can see that \eqref{linreg} is of the form in \eqref{conststep}. In this case $A_P$ is SPD.
In the linear regression setting, the error of a parameter $\theta$ is measured as the difference between the loss at the said parameter and the loss at the optimum, which has the following form
\begin{align*}
f(\theta)-f(\ts)=(\theta-\ts)^\top A_P (\theta-\ts)=\EE{\norm{\theta-\ts}^2_{A_P}}
\end{align*}

\subsection{Reinforcement Learning}
\end{comment}

\paragraph{RL Setting}
We are presented with data in the form of an $i.i.d$ sequence $(\phi_t,\phi'_t,r_t)\in \R^d\times\R^d\times \R$. Let $\gamma \in (0,1)$ be a fixed constant, we define $\Delta_t\eqdef \phi_t\phi_t^\top-\gamma \phi_t\phi_t^{'\top}$, $C_t=\phi_t\phi_t^\top$ and $b_t=\phi_r r_t$ the various temporal difference learning algorithms can be written as in \Cref{table:td}. In what follows, $\rho_t>0$ is an \emph{importance} sampling factor whose aim is to correct for mismatch in the (behavior) distribution with which the data was collected and the (target) distribution with respect to which one wants to learn. A factor $\rho_t=1,\,\forall t\geq 0$ will mean that no correction is required\footnote{This is known as the \emph{on-policy} case where the behavior is identical to the target. The general setting where $\rho_t>0$ is known as \emph{off-policy}.}.
\begin{comment}
\begin{table}

### 2017-05-06 uniform.tex
initial version

\section{Uniform stepsizes}
\begin{definition}
Call a set of distributions $\P$ over $\C^{\ncn}$
\emph{weakly admissible} if there exists $\alpha>0$ such that
$\rhos{P}>0$ holds for all $P\in \P$.
\end{definition}
\begin{definition}
Call a set of distributions $\P$ over $\C^{\ncn}$ \emph{admissible}
if there exists some $\alpha>0$ such that $\inf_{P\in \P} \rhos{P}>0$.
The value of $\alpha$ is called a witness.
\end{definition}
It is easy to see that $\alpha \mapsto \rhos{P}$ is decreasing,
hence if $\alpha>0$ witnesses that $\P$ is (weakly) admissible
then any $0<\alpha'\le \alpha$ is also witnessing this.

If $\P$ is weakly admissible, then one can choose a stepsize $\alpha>0$ solely based on the knowledge of $\P$ and
conclude that no matter the joint distribution of $(A_t,b_t)$, as long as the distribution of $A_t$ is an element of $\P$, the conclusions of \cref{maintheorem} hold. Further, if $\P$ is admissible then the error bound stated in  \cref{maintheorem} becomes independent of the instance.
Hence, an interesting question to investigate is whether a given set $\P$ is (weakly) admissible.
A hopeful set is the following:
For $B>0$, let $\P_B$ be the set of distributions over $\C_B^{\ncn}$ where for every $P\in \P_B$ is positive definite.
In what follows all distributions will be a subset of $\P_B$ with some $B>0$,
Note that in most applications the knowledge of a suitable $B>0$ such that $\P\subset \P_B$ is available.
By appropriately normalizing the matrices involved, we may as well assume that $B=1$.

Our first result shows that we cannot be too ambitious:
\begin{proposition}\label{notwad}
The set $\P_1$ is not weakly admissible.
\end{proposition}
\begin{proof}
Fix an arbitrary $\alpha>0$. We show that there exists $P\in \P$ such that $\rho_\alpha(P)<0$.
For $\epsilon \in (0,1/2)$ let $P$ be the distribution that is supported on $\{-I,I\}$ and takes on the value of $I$ with probability $1/2+\epsilon$. Then $A_P = 2\epsilon I \succ 0$, hence $P\in \P_1$. Further, $Q_P = I$.
Hence, $\rhos{P} = 4\epsilon-\alpha$. Hence, if $\epsilon<\alpha/4$, $\rho_\alpha(P)<0$.
\end{proof}
Thus \Cref{notwad} positive definiteness of $P\in \P_B$ alone is not sufficient for weak admissibility.
In linear least-squares problems (cf. \cref{ex:leastsquares}) the set $\P$ has more structure.
In particular, the random matrices $\{A_t\}$ are PSD. \todoc{The standard notation is $\mathrm{S}^{++}$ for the set of positive definite matrices. Introduce these and use them below..}
Define
\begin{align*}
\P_{\text{PSD},B} = \{ P \in \P_B \,:\,  \supp(P)\subset \text{PSD} \}\,.
\end{align*}
We have the following proposition:
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is weakly admissible
and in particular any $0<\alpha < 2/B$ witnesses this.
\end{proposition}
\begin{proof}
Take any $P\in \P_{\text{PSD}}$ and let $H\sim P$.
Consider the SVD of $H$: $H = U \Lambda U^\top$ where $U$ is orthonormal and $\Lambda$ is diagonal with
nonnegative elements. Note that $\Lambda \preceq B\, \I$ and thus $\Lambda^2 \preceq B \Lambda$.
Then for any $x\in \R^n$, $x^\top H^\top H x = x^\top U \Lambda^2 U^\top x \le B x^\top U \Lambda U^\top x = B x^\top H x$.
Taking expectations we find that $x^\top Q_P x \le B x^\top H_P x$.
Hence, $\rho_\alpha(P) = 2 x^\top H_P x - \alpha x^\top Q_P x \ge (2- \alpha B ) \,x^\top H_P x $.
Thus, for any $\alpha<2/B$, $\rho_\alpha(P)>0$.
\end{proof}
\todoc[inline]{So this altogether is weaker than what Bach founds. They prove strong admissibility.
I am guessing that for this they use that the loss is special and also that the noise is special.
This would be a good place to somehow incorporate this with a (short?) proof.
}

>>>>

\section{Uniform stepsizes}
\begin{definition}
Call a set of distributions $\P$ over $\C^{\dcd}$
\emph{weakly admissible} if there exists $\alpha>0$ such that
$\rhos{P}>0$ holds for all $P\in \P$.
\end{definition}
\begin{definition}
Call a set of distributions $\P$ over $\C^{\dcd}$ \emph{admissible}
if there exists some $\alpha>0$ such that $\inf_{P\in \P} \rhos{P}>0$.
The value of $\alpha$ is called a witness.
\end{definition}
It is easy to see that $\alpha \mapsto \rhos{P}$ is decreasing,
hence if $\alpha>0$ witnesses that $\P$ is (weakly) admissible
then any $0<\alpha'\le \alpha$ is also witnessing this.

If $\P$ is weakly admissible, then one can choose a stepsize $\alpha>0$ solely based on the knowledge of $\P$ and
conclude that no matter the joint distribution of $(A_t,b_t)$, as long as the distribution of $A_t$ is an element of $\P$, the conclusions of \cref{maintheorem} hold. Further, if $\P$ is admissible then the error bound stated in  \cref{maintheorem} becomes independent of the instance.
Hence, an interesting question to investigate is whether a given set $\P$ is (weakly) admissible.
A hopeful set is the following:
For $B>0$, let $\P_B$ be the set of distributions over $\C_B^{\dcd}$ where for every $P\in \P_B$ is positive definite.
In what follows all distributions will be a subset of $\P_B$ with some $B>0$,
Note that in most applications the knowledge of a suitable $B>0$ such that $\P\subset \P_B$ is available.
By appropriately normalizing the matrices involved, we may as well assume that $B=1$.

Our first result shows that we cannot be too ambitious:
\begin{proposition}\label{notwad}
The set $\P_1$ is not weakly admissible.
\end{proposition}
\begin{proof}
Fix an arbitrary $\alpha>0$. We show that there exists $P\in \P$ such that $\rho_\alpha(P)<0$.
For $\epsilon \in (0,1/2)$ let $P$ be the distribution that is supported on $\{-I,I\}$ and takes on the value of $I$ with probability $1/2+\epsilon$. Then $A_P = 2\epsilon I \succ 0$, hence $P\in \P_1$. Further, $Q_P = I$.
Hence, $\rhos{P} = 4\epsilon-\alpha$. Hence, if $\epsilon<\alpha/4$, $\rho_\alpha(P)<0$.
\end{proof}
Thus \Cref{notwad} positive definiteness of $P\in \P_B$ alone is not sufficient for weak admissibility.
In linear least-squares problems (cf. \cref{ex:leastsquares}) the set $\P$ has more structure.
In particular, the random matrices $\{A_t\}$ are PSD. \todoc{The standard notation is $\mathrm{S}^{++}$ for the set of positive definite matrices. Introduce these and use them below..}
Define
\begin{align*}
\P_{\text{PSD},B} = \{ P \in \P_B \,:\,  \supp(P)\subset \text{PSD} \}\,.
\end{align*}
We have the following proposition:
\begin{proposition}
For any $B>0$, the set $\P_{\text{PSD},B}$ is weakly admissible
and in particular any $0<\alpha < 2/B$ witnesses this.
\end{proposition}
\begin{proof}
Take any $P\in \P_{\text{PSD}}$ and let $H\sim P$.
Consider the SVD of $H$: $H = U \Lambda U^\top$ where $U$ is orthonormal and $\Lambda$ is diagonal with
nonnegative elements. Note that $\Lambda \preceq B\, \I$ and thus $\Lambda^2 \preceq B \Lambda$.
Then for any $x\in \R^d$, $x^\top H^\top H x = x^\top U \Lambda^2 U^\top x \le B x^\top U \Lambda U^\top x = B x^\top H x$.
Taking expectations we find that $x^\top Q_P x \le B x^\top H_P x$.
Hence, $\rho_\alpha(P) = 2 x^\top H_P x - \alpha x^\top Q_P x \ge (2- \alpha B ) \,x^\top H_P x $.
Thus, for any $\alpha<2/B$, $\rho_\alpha(P)>0$.
\end{proof}
\todoc[inline]{So this altogether is weaker than what Bach founds. They prove strong admissibility.
I am guessing that for this they use that the loss is special and also that the noise is special.
This would be a good place to somehow incorporate this with a (short?) proof.
}
